Subject-level developmental relationships

### 2024-09-15 1_get_data.qmd
more progress

```{r}
d_trial |>
  group_by(dataset_name) |>
  summarise(n = n(), 
            avg_acc_short = mean(short_window_accuracy, na.rm=TRUE),
            avg_acc_long = mean(long_window_accuracy, na.rm=TRUE),
            avg_rt = mean(rt, na.rm=TRUE),
            nas_in_acc_short = mean(is.na(short_window_accuracy)),
            nas_in_acc_long = mean(is.na(long_window_accuracy)),
            average_prop_data_short = mean(short_window_prop_data, na.rm=TRUE),
            average_prop_data_long = mean(long_window_prop_data, na.rm=TRUE),
            prop_rts = mean(!is.na(rt))) |>
  arrange(desc(n)) |>
  kable(digits = 2)
```

>>>>

```{r}
d_trial |>
  group_by(dataset_name) |>
  summarise(n = n(), 
            avg_acc_short = mean(short_window_accuracy, na.rm=TRUE),
            avg_acc_long = mean(long_window_accuracy, na.rm=TRUE),
            avg_rt = mean(rt, na.rm=TRUE),
            nas_in_acc_short = mean(is.na(short_window_accuracy)),
            nas_in_acc_long = mean(is.na(long_window_accuracy)),
            average_prop_data_short = mean(short_window_prop_data, na.rm=TRUE),
            average_prop_data_long = mean(long_window_prop_data, na.rm=TRUE),
            prop_rts = mean(!is.na(rt)), 
            log_age = log(age)) |>
  arrange(desc(n)) |>
  kable(digits = 2)
```

### 2024-09-15 2_developmental_analysis.qmd
more progress

```{r}
suppressPackageStartupMessages(library(here))
source(here("helper","common.R"))
d_trial <- readRDS(here("cached_intermediates","1_d_trial.Rds"))
d_sub <- readRDS(here("cached_intermediates","1_d_sub.Rds"))
```

@@

# Trial-level, across datasets

@@

```{r}
d_trial |>
ggplot(aes(x = age, y = rt)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  scale_x_log10() +
  scale_y_log10()
```

# Trial-level, for each dataset

@@

@@

# Participant-level, across datasets

@@

```{r}
d_sub |>
  pivot_longer(contains("accuracy"), 
               values_to = "accuracy", names_to = "measure") |>
ggplot(aes(x = age, y = accuracy)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  geom_hline(yintercept = .5, lty = 2) + 
  scale_x_log10() + 
  facet_wrap(~measure)
```

RT - but is it the mean of the log or the log of the mean? We choose log of the mean because this fits a log-normal distribution.

```{r}
d_sub |>
ggplot(aes(x = age, y = log_rt)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  scale_x_log10()  + 
  ylab("mean log RT")
```

# Participant-level, for each dataset

@@

```{r}
ggplot(d_sub_agevar, aes(x = age, y = short_window_elogit)) + 
  geom_point(alpha = .05) + 
  geom_smooth(method = "lm", col = "green", alpha = .5) +
  geom_smooth(method = "loess", alpha = .5) +
  geom_hline(yintercept = .5, lty = 2) + 
  scale_x_log10() + 
  facet_wrap(~dataset_name, scales = "free_x")
```

@@

>>>>

```{r}
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(broom.mixed))

source(here("helper","common.R"))
d_trial <- readRDS(here("cached_intermediates","1_d_trial.Rds")) |>
  mutate(log_age = log(age))
d_sub <- readRDS(here("cached_intermediates","1_d_sub.Rds"))
```

@@

# Trial-level

## Across datasets

@@

```{r}
d_trial |>
  pivot_longer(c("rt","log_rt"), 
               values_to = "rt", names_to = "measure") |>
  ggplot(aes(x = age, y = rt)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  scale_x_log10() +
  facet_wrap(~measure, scales = "free_y")
```
### Stats

Accuracy models.

```{r}
acc_mods <- list(lwe_lin = lm(long_window_elogit ~ age, data = d_trial),
                 lwe_log = lm(long_window_elogit ~ log_age, data = d_trial),
                 swe_lin = lm(short_window_elogit ~ age, data = d_trial),
                 swe_log = lm(short_window_elogit ~ log_age, data = d_trial),
                 lwa_lin = lm(long_window_accuracy ~ age, data = d_trial),
                 lwa_log = lm(long_window_accuracy ~ log_age, data = d_trial),
                 swa_lin = lm(short_window_accuracy ~ age, data = d_trial),
                 swa_log = lm(short_window_accuracy ~ log_age, data = d_trial))

acc_mods_summary <- map_df(acc_mods, ~broom::glance(.x)) |>
  mutate(model = names(acc_mods))

kable(acc_mods_summary, digits = 4)
```

Reaction time models.

```{r}
rt_mods <- list(log_log = lm(log_rt ~ log_age, data = d_trial),
                log_lin = lm(log_rt ~ age, data = d_trial),
                lin_log = lm(rt ~ log_age, data = d_trial),
                lin_lin = lm(rt ~ age, data = d_trial))

rt_mods_summary <- map_df(rt_mods, ~broom::glance(.x)) |>
  mutate(model = names(rt_mods))

kable(rt_mods_summary, digits = 4)
```

## Within dataset

@@

Accuracy

@@

### Stats

Accuracy models. This time LMERs.

```{r}
d_trial$age_s <- scale(d_trial$age)[,1]
d_trial$log_age_s <- scale(d_trial$log_age)[,1]

acc_mods_lmer <- list(lwe_lin = lmer(long_window_elogit ~ 1 
                                     + (age_s | dataset_name), data = d_trial),
                      lwe_log = lmer(long_window_elogit ~ 1
                                     + (log_age_s | dataset_name), data = d_trial),
                      swe_lin = lmer(short_window_elogit ~ 1
                                     + (age_s | dataset_name), data = d_trial),
                      swe_log = lmer(short_window_elogit ~ 1
                                     + (log_age_s | dataset_name), data = d_trial),
                      lwa_lin = lmer(long_window_accuracy ~ 1
                                     + (age_s | dataset_name), data = d_trial),
                      lwa_log = lmer(long_window_accuracy ~ 1
                                     + (log_age_s | dataset_name), data = d_trial),
                      swa_lin = lmer(short_window_accuracy ~ 1
                                     + (age_s | dataset_name), data = d_trial),
                      swa_log = lmer(short_window_accuracy ~ 1
                                     + (log_age_s | dataset_name), data = d_trial))

acc_mods_lmer_summary <- map_df(acc_mods_lmer, ~broom.mixed::glance(.x)) |>
  mutate(model = names(acc_mods_lmer), 
         r2 = map_dbl(acc_mods_lmer, ~performance::r2_nakagawa(.x)$R2_conditional))

kable(acc_mods_lmer_summary, digits = 4)
```

Reaction time models.

```{r}
rt_mods_lmer <- list(log_log = lmer(log_rt ~ 1 + 
                                      (log_age_s | dataset_name), data = d_trial),
                     log_lin = lmer(log_rt ~ 1 + 
                                      (age_s | dataset_name), data = d_trial),
                     lin_log = lmer(rt ~ 1 + 
                                      (log_age_s | dataset_name), data = d_trial),
                     lin_lin = lmer(rt ~ 1 + 
                                      (age_s | dataset_name), data = d_trial))

rt_mods_lmer_summary <- map_df(rt_mods_lmer, ~broom.mixed::glance(.x)) |>
  mutate(model = names(rt_mods_lmer), 
         r2 = map_dbl(rt_mods_lmer, ~performance::r2_nakagawa(.x)$R2_conditional))

kable(rt_mods_lmer_summary, digits = 4)
```

# Participant-level

## Across datasets

@@

```{r}
d_sub_long <- d_sub |>
  pivot_longer(contains("accuracy"), 
               values_to = "accuracy", names_to = "measure") 
d_sub_agevar_long <- d_sub_agevar |>
  pivot_longer(contains("accuracy"), 
               values_to = "accuracy", names_to = "measure")

ggplot(d_sub_long, 
       aes(x = age, y = accuracy)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  geom_smooth(data = d_sub_agevar_long,
              aes(group = dataset_name, col = dataset_name), geom="line",
              alpha = .1, method = "lm", size = .5, lty = 2) + 
  geom_hline(yintercept = .5, lty = 2) + 
  scale_x_log10() + 
  facet_wrap(~measure) + 
  theme(legend.position = "bottom") + 
  ylab("Accuracy") + 
  xlab("Age (months)")
```

Elogits

```{r}
d_sub_long_elogit <- d_sub |>
  pivot_longer(contains("elogit"), 
               values_to = "accuracy", names_to = "measure") 
d_sub_agevar_long_elogit <- d_sub_agevar |>
  pivot_longer(contains("elogit"), 
               values_to = "accuracy", names_to = "measure")

ggplot(d_sub_long_elogit, 
       aes(x = age, y = accuracy)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  geom_smooth(data = d_sub_agevar_long_elogit,
              aes(group = dataset_name, col = dataset_name), geom="line",
              alpha = .1, method = "lm", size = .5, lty = 2) + 
  geom_hline(yintercept = .5, lty = 2) + 
  scale_x_log10() + 
  facet_wrap(~measure) + 
  theme(legend.position = "bottom") + 
  ylab("Accuracy (elogit)") + 
  xlab("Age (months)")
```

RTs

```{r}
d_sub_long_rt <- d_sub |>
  pivot_longer(c("rt","log_rt"), 
               values_to = "rt", names_to = "measure")

d_sub_agevar_long_rt <- d_sub_agevar |>
  pivot_longer(c("rt","log_rt"), 
               values_to = "rt", names_to = "measure")

ggplot(d_sub_long_rt, 
       aes(x = age, y = rt)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  geom_smooth(data = d_sub_agevar_long_rt,
              aes(group = dataset_name, col = dataset_name), geom="line",
              alpha = .1, method = "lm", size = .5, lty = 2) + 
  # geom_hline(yintercept = .5, lty = 2) + 
  scale_x_log10() + 
  facet_wrap(~measure, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  ylab("mean log RT") + 
  xlab("Age (months)")

```

### Stats

Accuracy models.

```{r}
acc_mods_sub <- list(lwe_lin = lm(long_window_elogit ~ age, data = d_sub),
                     lwe_log = lm(long_window_elogit ~ log_age, data = d_sub),
                     swe_lin = lm(short_window_elogit ~ age, data = d_sub),
                     swe_log = lm(short_window_elogit ~ log_age, data = d_sub),
                     lwa_lin = lm(long_window_accuracy ~ age, data = d_sub),
                     lwa_log = lm(long_window_accuracy ~ log_age, data = d_sub),
                     swa_lin = lm(short_window_accuracy ~ age, data = d_sub),
                     swa_log = lm(short_window_accuracy ~ log_age, data = d_sub))

acc_mods_sub_summary <- map_df(acc_mods_sub, ~broom::glance(.x)) |>
  mutate(model = names(acc_mods_sub))

kable(acc_mods_sub_summary, digits = 4)
```

Reaction time models.

```{r}
mods_sub <- list(log_log = lm(log_rt ~ log_age, data = d_sub),
                 log_lin = lm(log_rt ~ age, data = d_sub),
                 lin_log = lm(rt ~ log_age, data = d_sub),
                 lin_lin = lm(rt ~ age, data = d_sub))

models_sub <- map_df(mods_sub, ~broom::glance(.x)) |>
  mutate(model = names(mods_sub))

kable(models_sub, digits = 4)
```

## Within dataset

@@

```{r}
ggplot(d_sub_agevar, aes(x = age, y = long_window_elogit)) +
  geom_point(alpha = .05) +
  geom_smooth(method = "lm", col = "green", alpha = .5) +
  geom_smooth(method = "loess", alpha = .5) +
  geom_hline(yintercept = .5, lty = 2) +
  # scale_x_log10() +
  ylim(-2,3) + 
  facet_wrap(~dataset_name, scales = "free_x")
```

@@

### Stats

Accuracy models.

```{r}
d_sub$age_s <- scale(d_sub$age)[,1]
d_sub$log_age_s <- scale(d_sub$log_age)[,1]

acc_mods_sub_lmer <- list(lwe_lin = lmer(long_window_elogit ~ 1 
                                         + (age_s | dataset_name), data = d_sub),
                          lwe_log = lmer(long_window_elogit ~ 1
                                         + (log_age_s | dataset_name), data = d_sub),
                          swe_lin = lmer(short_window_elogit ~ 1
                                         + (age_s | dataset_name), data = d_sub),
                          swe_log = lmer(short_window_elogit ~ 1
                                         + (log_age_s | dataset_name), data = d_sub),
                          lwa_lin = lmer(long_window_accuracy ~ 1
                                         + (age_s | dataset_name), data = d_sub),
                          lwa_log = lmer(long_window_accuracy ~ 1
                                         + (log_age_s | dataset_name), data = d_sub),
                          swa_lin = lmer(short_window_accuracy ~ 1
                                         + (age_s | dataset_name), data = d_sub),
                          swa_log = lmer(short_window_accuracy ~ 1
                                         + (log_age_s | dataset_name), data = d_sub))

acc_mods_sub_lmer_summary <- map_df(acc_mods_sub_lmer, ~broom.mixed::glance(.x)) |>
  mutate(model = names(acc_mods_sub_lmer), 
         r2 = map_dbl(acc_mods_sub_lmer, ~performance::r2_nakagawa(.x)$R2_conditional))

kable(acc_mods_sub_lmer_summary, digits = 4)
```

Reaction time models.

```{r}
rt_mods_lmer <- list(log_log = lmer(log_rt ~ 1 + 
                                      (log_age_s | dataset_name), data = d_sub),
                     log_lin = lmer(log_rt ~ 1 + 
                                      (age_s | dataset_name), data = d_sub),
                     lin_log = lmer(rt ~ 1 + 
                                      (log_age_s | dataset_name), data = d_sub),
                     lin_lin = lmer(rt ~ 1 + 
                                      (age_s | dataset_name), data = d_sub))

rt_mods_lmer_summary <- map_df(rt_mods_lmer, ~broom.mixed::glance(.x)) |>
  mutate(model = names(rt_mods_lmer), 
         r2 = map_dbl(rt_mods_lmer, ~performance::r2_nakagawa(.x)$R2_conditional))

kable(rt_mods_lmer_summary, digits = 4)
```

# Variability

```{r}
d_var <- d_trial |>
  group_by(dataset_name, administration_id, age) |>
  summarise (`SD(log RT)` = sd(log_rt, na.rm=TRUE), 
             `SD(accuracy)` = sd(long_window_elogit, na.rm=TRUE)) |>
  pivot_longer(contains("sd"), 
               values_to = "sd", names_to = "measure")

v <- ggplot(d_var, aes(x = age, y = sd)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  geom_smooth(data = d_var |>
  filter(dataset_name %in% datasets_with_age_variation$dataset_name),
              aes(group = dataset_name, col = dataset_name), geom="line",
              alpha = .1, method = "lm", size = .5, lty = 2) + 
  scale_color_discrete(guide = FALSE) + 
  scale_x_log10() +
  facet_wrap(~measure, scales = "free_y")

v 
ggsave(v, filename = "figures/var.png", width = 8, height = 3.5)

```
# Pub stuff

stats

```{r}
d_sub |>
  group_by(dataset_name) |>
  summarise(n = n(), 
            `Mean Age` = mean(age), 
            `Min Age` = min(age), 
            `Max Age` = max(age), 
            `CDIs` = ifelse(!is.na(any(prod)), "x", ""), 
            `longitudinal` = ifelse(any(duplicated(subject_id)), "x", "")) |>
  xtable(caption = "Characteristics of included datasets from Peekbank.")
```

```{r}
a <- ggplot(d_sub_long_elogit |> filter(measure == "long_window_elogit"), 
       aes(x = age, y = accuracy)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  geom_smooth(data = d_sub_agevar_long_elogit |> filter(measure == "long_window_elogit"),
              aes(group = dataset_name, col = dataset_name), geom="line",
              alpha = .1, method = "lm", size = .5, lty = 2) + 
  geom_hline(yintercept = .5, lty = 2) + 
  scale_x_log10() +
  scale_color_discrete(guide = FALSE) + 
  ylab("Accuracy (elogit)") + 
  xlab("Age (months)")

b <- ggplot(d_sub_long_rt |> filter(measure == "log_rt"), 
       aes(x = age, y = rt)) + 
  geom_point(alpha = .05) + 
  geom_smooth() +
  geom_smooth(method = "lm", col = "green") +
  geom_smooth(data = d_sub_agevar_long_rt |> filter(measure == "log_rt"),
              aes(group = dataset_name, col = dataset_name), geom="line",
              alpha = .1, method = "lm", size = .5, lty = 2) + 
  # geom_hline(yintercept = .5, lty = 2) + 
  scale_x_log10() +
  scale_color_discrete(guide = FALSE) + 
  theme(legend.position = "bottom") + 
  ylab("Reaction Time (log)") + 
  xlab("Age (months)")

f <- cowplot::plot_grid(a,b)
ggsave(f, filename = "figures/acc_rt.png", width = 8, height = 3.5)

```

### 2024-09-15 3_developmental_relationships.qmd
more progress

# Relation between RT and accuracy

@@

Let's select the best of these.

```{r, fig.width=9, fig.height=9}
GGally::ggpairs(select(d_sub, log_age, rt,  
                       long_window_accuracy, short_window_accuracy, prod, comp), 
                progress = FALSE, lower = list(continuous = GGally::wrap("points", alpha = 0.03)))

@@

@@

```{r}
datasets_with_age_variation <- d_trial |>
  group_by(dataset_name) |>
  summarise(age_range = max(age) - min(age)) |>
  filter(age_range >= 6)

@@

Make into matrices and look at PCA

```{r}
d_sub_mat <- d_sub |>
  ungroup() |>
  select(log_age, rt,  long_window_accuracy, prod)

@@

@@

@@

```{r}
mod1 <- fa(d_sub_mat, 1)
mod2 <- fa(d_sub_mat, 2)
```

```{r}
fa.parallel(d_sub_mat)
```

```{r}
d_sub_mat_comp <- d_sub |>
  ungroup() |>
  select(log_age, rt,  long_window_accuracy, comp)

acc_rt_prc_comp <- prcomp(x = d_sub_mat_comp, scale = TRUE)

@@

```{r}
mod1_comp <- fa(d_sub_mat_comp, 1)
mod2_comp <- fa(d_sub_mat_comp, 2)
```

>>>>

# Relations between variables

## Between datasets

```{r}
cor(select(d_sub, age, log_age, rt, log_rt, 
                       short_window_accuracy, long_window_accuracy, 
                       short_window_elogit, long_window_elogit, prod, comp), 
    use = "pairwise.complete.obs") |>
  round(2)
```

@@

Let's select the most interesting of these.

```{r, fig.width=9, fig.height=9}
d_sub |>
  select(log_age, log_rt,  
         long_window_accuracy,  prod, comp) |>
GGally::ggpairs(progress = FALSE, 
                lower = list(continuous = GGally::wrap("points", alpha = 0.03)))

@@

## Within dataset

All the variables.

```{r}
all_corrs <- d_sub |>
select(dataset_name, age, log_age, rt, log_rt, 
                       short_window_accuracy, long_window_accuracy, 
                       short_window_elogit, long_window_elogit, prod, comp) |>
  group_by(dataset_name) |>
  nest() |>
  mutate(corrs = map(data, ~cor(.x, use = "pairwise.complete.obs")),
         long_corrs = map(corrs, ~pivot_longer(as_tibble(.x) |> 
                                                mutate(variable1 = colnames(.x)), 
                                               -variable1, names_to = "variable2", 
                                               values_to = "r"))) |>
  select(-data, -corrs) |>
  unnest(cols = c(long_corrs))

ggplot(all_corrs, aes(x = variable1, y = r, col = dataset_name)) + 
  geom_point(alpha = .2) + 
  stat_summary(fun.data = "mean_cl_boot", col = "black") +
  coord_flip() + 
  facet_wrap(~variable2)
```

Several variables.

```{r}
d_sub_agevar <- d_sub |>
  filter(dataset_name %in% datasets_with_age_variation$dataset_name)

all_corrs <- d_sub_agevar |>
select(dataset_name, log_age, log_rt, rt,
                       long_window_accuracy, long_window_elogit) |>
  group_by(dataset_name) |>
  nest() |>
  mutate(corrs = map(data, ~cor(.x, use = "pairwise.complete.obs")),
         long_corrs = map(corrs, ~pivot_longer(as_tibble(.x) |> 
                                                mutate(variable1 = colnames(.x)), 
                                               -variable1, names_to = "variable2", 
                                               values_to = "r"))) |>
  select(-data, -corrs) |>
  unnest(cols = c(long_corrs)) |>
  filter(variable1 != variable2, 
         !(variable1 == "rt" & variable2 == "log_rt"), 
         !(variable1 == "log_rt" & variable2 == "rt"),
         !(variable1 == "long_window_accuracy" & variable2 == "long_window_elogit"),
         !(variable1 == "long_window_elogit" & variable2 == "long_window_accuracy"))

ggplot(all_corrs,
       aes(x = variable1, y = r, col = dataset_name)) + 
  geom_point(alpha = .5, pch = 20) +
  stat_summary(fun.data = "mean_cl_boot", aes(group = 1)) +
  geom_hline(yintercept = 0, lty = 2) + 
  # coord_flip() +
  facet_grid(.~variable2, scales = "free_x") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Plot correlations of key variables now.  Annoying to figure out how to remove the upper diagonal...

```{r}
all_corrs <- d_sub_agevar |>
select(dataset_name, log_age, log_rt,
                       long_window_accuracy) |>
  group_by(dataset_name) |>
  nest() |>
  mutate(corrs = map(data, ~cor(.x, use = "pairwise.complete.obs")),
         long_corrs = map(corrs, ~pivot_longer(as_tibble(.x) |> 
                                                mutate(variable1 = colnames(.x)), 
                                               -variable1, names_to = "variable2", 
                                               values_to = "r"))) |>
  select(-data, -corrs) |>
  unnest(cols = c(long_corrs)) |>
  filter(variable1 != variable2)

ggplot(all_corrs,
       aes(x = interaction(variable1, variable2), y = r, col = dataset_name)) + 
  geom_point(alpha = .5, pch = 20) +
  stat_summary(fun.data = "mean_cl_boot", aes(group = 1)) +
  geom_hline(yintercept = 0, lty = 2) + 
  coord_flip() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

```{r}
datasets_with_age_variation <- d_trial |>
  group_by(dataset_name) |>
  summarise(age_range = max(age) - min(age)) |>
  filter(age_range >= 4)

@@

```{r}
d_sub_mat <- d_sub |>
  ungroup() |>
  select(log_age, log_rt, long_window_elogit, prod)

@@

fa.parallel(d_sub_mat)
```

Factor analysis first. This is probably more appropriate.

```{r}
mod1 <- fa(d_sub_mat, 1, rotate = "varimax")
mod2 <- fa(d_sub_mat, 2, rotate = "varimax")

summary(mod1)
mod1
```

Make into matrices and look at PCA.

@@

## Production within individual datasets

```{r}
d_sub_mat_dataset <- d_sub |>
  filter(dataset_name %in% datasets_with_age_variation$dataset_name) |>
  group_by(dataset_name) |>
  select(dataset_name, log_age, log_rt, long_window_elogit, prod)

d_sub_mat_grp <- d_sub_mat_dataset |>
  nest() |>
  mutate(complete_data = map(data, ~filter(.x[complete.cases(.x),])),
    mat = as.matrix(complete_data), 
    has_data = map_lgl(complete_data, ~nrow(.x)>0)) |>
  filter(has_data) |>
  mutate(factors = map(mat, ~fa(.x, 1, rotate = "varimax")), 
         f_summary = map(factors, summary), 
         loadings = map_df(factors, ~as.tibble(loadings(x))))

d_sub_mat_grp |>

```{r}
d_sub_mat_comp <- d_sub |>
  ungroup() |>
  select(log_age, log_rt,  long_window_elogit, comp)

Scree.

@@

```{r}
mod1_comp <- fa(d_sub_mat_comp, 1, rotate = "varimax")
mod2_comp <- fa(d_sub_mat_comp, 2, rotate = "varimax")

summary(mod1_comp)
loadings(mod1_comp)
```

PCA.

```{r}
acc_rt_prc_comp <- prcomp(x = d_sub_mat_comp, scale = TRUE)

@@
